### 2014-06-06 paper/body.tex
small edits

\section{Generality vs. Specificity as transfer from one dataset to another}
\label{sec:definition}

We have noted the curious tendency of Gabor features to show up in the first layer of neural networks trained on natural images for a large range of network architectures and cost functions. We say these features are general if they are useful for many different tasks or specific if they are useful only for a few. We can measure the specificity of a set of features by training it on one task \dA and then using it for another task \dB.

Of course, this definition depends on the distance between \dA and \dB. In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset.  \edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.

>>>>

\section{Generality vs. specificity measured as transfer performance}
\label{sec:definition}

We have noted the curious tendency of Gabor features to show up in the first layer of neural networks trained on natural images for a large range of network architectures and cost functions. We say these features are general if they are useful for many different tasks or specific if they are useful only for a few. We can measure the specificity of a set of features by training the set on one task \dA and then using the feature set for another task \dB.

Of course, this definition depends on the similarity, or distance, between \dA and \dB. In this paper, we take tasks \dA and \dB to be classifying different, non-overlapping subsets of a particular dataset.  These subsets could be chosen such that they are similar (e.g. by randomly splitting a large dataset into two smaller datasets), or they could be chosen to be different (e.g. by choosing the subsets to be maximally different). 
%This is only one possible way of sampling tasks \dA and \dB.
